---
title: "Exploratory Data Analysis"
author:
- Gabriel Lahman
- Rowan Lavelle
- Jordan Majoros
- Matthew Zelenin
date: "11/11/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(alr4)
library(ggplot2)
```

##Introduction

##SLIDE 1

Dr. Mary Beth Nebel created a study that examines the relationship between motor skills and social defecits within a given population of children. The children, aged 8 to 13, completed a motor skills assessment that tested manual dexterity, aiming and catching, and balance. The children also completed a test for intelligence, consisting of assessments of vocabularly, general knowledge, word similarities, block patterns, picture concepts, and matrix reasoning with pictures. 

In terms of scientific context, this experiment provides an insight as to whether you can predict a child's social deficit based on their motor abilities. This would allow another insight as to predicting a child's social deficits and possible disorders. 

The two main social disorders that are examined in this study are ADHD and Autism. These disorders halter someone's 

Autism and ADHD can be difficult to diagnose, as there is no one set medical test. There are methods of diagnosis, which center primarily about the environment of the child and their social behaviors, not as much regarding solidified quantifiable data. 

##SLIDE 2

## Research Question

Is there a statistically significant difference in predictive power of the motor skills vs. social responsivness model when we include intelligence metrics as predictors?

- discuss which variables are beneficial to answering this research question
  - mABC_TotalStandardScore - motor skills
  - WISC scores - the intelligence metrics
  - SRS_TotalRawAScore - the social responsiveness scale, what we are trying to predict


- key variables that were collected
- describe the disorders being discovered

## Filtering Data

```{r message=FALSE, warning=FALSE}

kki_demographics = read.csv('data/KKI_demographicInfo.csv')
kki_handedness = read.csv('data/KKI_handedness.csv')
kki_mABC = read.csv('data/KKI_movementAssessmentBatteryforChildren.csv')
kki_SRS = read.csv('data/KKI_SocialResponsivenessScaleQuestionnaire.csv')
kki_WISC = read.csv('data/KKI_WechslerIntelligenceScaleforChildren.csv')


full_dat = full_join(kki_demographics, kki_mABC)
full_dat = full_join(full_dat, kki_SRS)
full_dat = full_join(full_dat, kki_WISC)
full_dat = full_join(full_dat, kki_handedness)
full_dat = full_dat %>% drop_na(c('SecondaryDiagnosis', 'CurrentlyNotTakingMeds', 'CurrentlyTakingAtomoxetine', 'CurrentlyTakingClonidine', 'mABC_TotalStandardScore', 'EdinburghHandedness_Integer'))
full_dat = subset(full_dat, visit == 1)
full_dat = subset(full_dat, !is.na(WISC_VERSION) & !is.na(SRS_VERSION))
full_dat = subset(full_dat, ADHD_Subtype %in% c('Combined', 'Hyperactive/Impulsive', 'Inattentive', 'No dx'))
WISC4_full_dat = subset(full_dat, WISC_VERSION == 4)
WISC5_full_dat = subset(full_dat, WISC_VERSION == 5)
```

## Summarizing Data
```{r message=FALSE, warning=FALSE}
table(factor(full_dat$PrimaryDiagnosis), factor(full_dat$ADHD_Subtype))
table(factor(full_dat$WISC_VERSION))
table(factor(WISC4_full_dat$PrimaryDiagnosis), factor(WISC4_full_dat$ADHD_Subtype))
```

## Main Variables of Interest

### mABC_AGE
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=mABC_AGE, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=mABC_TotalStandardScore, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### SRS_TotalRawScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_Vocabulary
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_Vocabulary, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_Information
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_Information, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_Similarities
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_Similarities, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_BlockDesign
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_BlockDesign, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_PictureConcepts
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_PictureConcepts, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

### WISC4_MatrixReasoning
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=PrimaryDiagnosis, y=WISC4_MatrixReasoning, color=PrimaryDiagnosis)) + 
  geom_boxplot()
```

## Plots

### mABC_AGE vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x=mABC_AGE, y=mABC_TotalStandardScore)) + 
  geom_jitter() + 
  ggtitle('Age vs. mABC Total Standard Score')
```

### SRS_TotalRawScore vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(full_dat, aes(y=SRS_TotalRawScore, x=mABC_TotalStandardScore)) + 
  geom_jitter() + 
  ggtitle('SRS_TotalRawScore vs. mABC Total Standard Score')
```

### WISC4_Vocabulary vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_Vocabulary, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_Vocabulary vs. mABC Total Standard Score')
```

### WISC5_Vocabulary vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC5_full_dat, aes(x= WISC5_Vocabulary, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC5_Vocabulary vs. mABC Total Standard Score')
```

### WISC4_Information vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_Information, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_Information vs. mABC Total Standard Score')
```

### WISC4_Similarities vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_Similarities, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_Similarities vs. mABC Total Standard Score')
```

### WISC5_Similarities vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC5_full_dat, aes(x= WISC5_Similarities, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC5_Similarities vs. mABC Total Standard Score')
```

### WISC4_BlockDesign vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_BlockDesign, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_Design vs. mABC Total Standard Score')
```

### WISC4_PictureConcepts vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_PictureConcepts, y=mABC_TotalStandardScore)) +
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_PictureConcepts vs. mABC Total Standard Score')
```

### WISC4_MatrixReasoning vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_MatrixReasoning, y=mABC_TotalStandardScore)) +
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('WISC4_MatrixReasoning vs. mABC Total Standard Score')
```

### Scatterplot Matrix for WISC_4
```{r message=FALSE, warning=FALSE, fig.align='center'}
scatterplotMatrix(WISC4_full_dat[c('WISC4_Vocabulary', 'WISC4_Information', 'WISC4_Similarities', 'WISC4_BlockDesign', 'WISC4_PictureConcepts', 'WISC4_MatrixReasoning')], cex = 0.05)
```

### Scatterplot Matrix for WISC_5
```{r message=FALSE, warning=FALSE, fig.align='center'}
scatterplotMatrix(WISC5_full_dat[c('WISC5_Vocabulary', 'WISC5_Similarities', 'WISC5_BlockDesign', 'WISC5_MatrixReasoning', 'WISC5_FigureWeights')], cex = 0.5)
```

### log(WISC4_Information) vs. mABC Total Standard Score
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= log(WISC4_Information), y=mABC_TotalStandardScore)) + geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('log(WISC4_Information) vs. mABC Total Standard Score')
```

### WISC4_Total vs mABC_TotalStandardScore
```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(WISC4_full_dat, aes(x= WISC4_Vocabulary + WISC4_Information + WISC4_Similarities + WISC4_BlockDesign + WISC4_PictureConcepts + WISC4_MatrixReasoning, y=mABC_TotalStandardScore)) + 
  geom_jitter() +
  facet_grid(. ~ PrimaryDiagnosis) + 
  ggtitle('Sum of WISC4_Vars vs. mABC Total Standard Score')
```

