```{r}
library(dplyr)
library(tidyr)
library(alr4)
library(ggplot2)
library(gridExtra)

setwd('/Users/rowlavel/Documents/Classes/Fall2019/LinearModels/S431_KKI_data_analysis')

kki_demographics = read.csv('data/KKI_demographicInfo.csv')
kki_handedness = read.csv('data/KKI_handedness.csv')
kki_mABC = read.csv('data/KKI_movementAssessmentBatteryforChildren.csv')
kki_SRS = read.csv('data/KKI_SocialResponsivenessScaleQuestionnaire.csv')
kki_WISC = read.csv('data/KKI_WechslerIntelligenceScaleforChildren.csv')
kki_gai = read.csv('data/KKI_GAI_from_WISC.csv')


full_dat = full_join(kki_demographics, kki_mABC)
full_dat = full_join(full_dat, kki_SRS)
full_dat = full_join(full_dat, kki_WISC)
full_dat = full_join(full_dat, kki_handedness)
full_dat = full_join(full_dat, kki_gai)

full_dat = full_dat %>% drop_na(c('SecondaryDiagnosis', 
                                  'CurrentlyNotTakingMeds', 
                                  'CurrentlyTakingAtomoxetine', 
                                  'CurrentlyTakingClonidine', 
                                  'mABC_TotalStandardScore', 
                                  'EdinburghHandedness_Integer',
                                  'GAI'))
full_dat = subset(full_dat, visit == 1)
full_dat = subset(full_dat, !is.na(WISC_VERSION) & !is.na(SRS_VERSION))
full_dat = subset(full_dat, ADHD_Subtype %in% c('Combined', 
                                                'Hyperactive/Impulsive', 
                                                'Inattentive', 'No dx'))
nrow(full_dat)


full_dat = filter(full_dat, full_dat$PrimaryDiagnosis=='None')

full_dat$hasADHD = as.integer(full_dat$ADHD_Subtype != 'No dx')
full_dat$hasAutism = as.integer(full_dat$PrimaryDiagnosis == 'Autism')

WISC4_full_dat = subset(full_dat, WISC_VERSION == 4)
WISC5_full_dat = subset(full_dat, WISC_VERSION == 5)
```

```{r}
red_model = lm(SRS_TotalRawScore~mABC_TotalStandardScore, data=full_dat)
full_model = lm(SRS_TotalRawScore~
                  mABC_ManualDexterity.Component.StandardScore+
                  mABC_AimingAndCatching.Component.StandardScore+
                  mABC_Balance.Component.StandardScore,data=full_dat)
```

```{r}
summary(red_model)
summary(full_model)
```

```{r}
anova(red_model,full_model)
plot(density(full_dat$mABC_TotalStandardScore))
```
Reject null, take full model

```{r}
# full model includinfg GAI
none_model_full = lm(SRS_TotalRawScore~
                          mABC_ManualDexterity.Component.StandardScore+
                          mABC_AimingAndCatching.Component.StandardScore+
                          mABC_Balance.Component.StandardScore +
                          GAI + as.factor(SRS_VERSION)
                          ,data=full_dat)

# reduced model not including GAI
none_model_red = lm(SRS_TotalRawScore~
                         mABC_ManualDexterity.Component.StandardScore+
                         mABC_AimingAndCatching.Component.StandardScore+
                         mABC_Balance.Component.StandardScore + as.factor(SRS_VERSION)
                         ,data=full_dat)
```

```{r}
summary(none_model_full)
```

```{r}
summary(none_model_red)
```

```{r}
anova(none_model_full,none_model_red)
```
reject null, take full model 

```{r}
none_model_full$coefficients
```

```{r}
full_dat$none_predict = predict(full_model)

ggplot(data=full_dat, aes(x=mABC_TotalStandardScore,y=SRS_TotalRawScore,col=as.factor(SRS_VERSION))) + 
  geom_jitter(alpha=0.3,width=0.2,height=0.2) + 
  geom_abline(slope=none_model_full$coefficients[2],
              intercept=none_model_full$coefficients[1], 
              col='red') +
  geom_abline(slope=none_model_full$coefficients[2],
              intercept=none_model_full$coefficients[1]+none_model_full$coefficients[6], 
              col='blue') + 
  xlab('mABC Total Score') +
  ylab('SRS Total Score') +
  ggtitle('Marginal Plot, mABC ManualDexterity Component Standard Score vs. SRS Total Score')

ggplot(full_dat, aes(x=none_predict, y=resid(none_model_full), col=as.factor(SRS_VERSION))) + geom_point()
qqnorm(resid(none_model_full))

resid = residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SRS_VERSION, data = full_dat))
GAI_regout = residuals(lm(GAI~ mABC_TotalStandardScore + SRS_VERSION, data=full_dat))
qplot(x = GAI_regout, y = resid) + geom_smooth(method='lm') + 
  xlab('GAI (prior model regressed out)') +
  ylab('SRS Total Score (prior model residuals)') +
  ggtitle('Added Variable Plot, GAI vs. SRS Total Score')

man_dext_regout_tss = residuals(lm(mABC_ManualDexterity.Component.StandardScore ~ mABC_TotalStandardScore + SRS_VERSION, data = full_dat))
qplot(x = man_dext_regout_tss, y = resid) + geom_smooth(method='lm') + 
  xlab('Manual Dexterity (prior model regressed out)') +
  ylab('SRS Total Score (prior model residuals)') +
  ggtitle('Added Variable Plot, Manual Dexterity vs. SRS Total Score')

aim_catch_regout_tss = residuals(lm(mABC_AimingAndCatching.Component.StandardScore ~ mABC_TotalStandardScore + SRS_VERSION, data = full_dat))
qplot(x = aim_catch_regout_tss, y = resid) + geom_smooth(method='lm') + 
  xlab('Aiming and Catching (prior model regressed out)') +
  ylab('SRS Total Score (prior model residuals)') +
  ggtitle('Added Variable Plot, Aiming and Catching vs. SRS Total Score')

balance_regout_tss = residuals(lm(mABC_Balance.Component.StandardScore ~ mABC_TotalStandardScore + SRS_VERSION, data = full_dat))
qplot(x = balance_regout_tss, y = resid) + geom_smooth(method='lm') + 
  xlab('Balance (prior model regressed out)') +
  ylab('SRS Total Score (prior model residuals)') +
  ggtitle('Added Variable Plot, Balance vs. SRS Total Score')

age_regout_tss = residuals(lm(mABC_AGE ~ mABC_TotalStandardScore + SRS_VERSION, data = full_dat))
qplot(x = age_regout_tss, y = resid) + geom_smooth(method='lm') + 
  xlab('Agee (prior model regressed out)') +
  ylab('SRS Total Score (prior model residuals)') +
  ggtitle('Added Variable Plot, Age vs. SRS Total Score')
```

Should we include gender?
```{r}
red = lm(SRS_TotalRawScore~
           mABC_ManualDexterity.Component.StandardScore+
           mABC_AimingAndCatching.Component.StandardScore+
           mABC_Balance.Component.StandardScore , data=full_dat)

full = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore +
            as.factor(Gender), data=full_dat)
anova(red,full)
```
no, Dont reject null keep reduced model

Should we keep age?
```{r}
red = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore, data=full_dat)

full = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore +
            mABC_AGE, data=full_dat)
anova(red,full)
```
No, Dont reject null keep reduced model

Should we take GAI?
```{r}
red = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore, data=full_dat)

full = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore+
            GAI, data=full_dat)
anova(red,full)
```
yes, reject null, take full model

Should we take version?
```{r}
red = lm(SRS_TotalRawScore~
           mABC_ManualDexterity.Component.StandardScore+
           mABC_AimingAndCatching.Component.StandardScore+
           mABC_Balance.Component.StandardScore,data=full_dat)
full = lm(SRS_TotalRawScore~
            mABC_ManualDexterity.Component.StandardScore+
            mABC_AimingAndCatching.Component.StandardScore+
            mABC_Balance.Component.StandardScore+
            as.factor(SRS_VERSION),data=full_dat)
anova(red,full)
```
yes, reject null, take full model


$$

y_i = \beta_0 + \beta_1 d_0 + \beta_2 X_1 + \beta_3 X_2 + \beta_4 X_3 + \beta_5 X_4\ \\

d_0 = \begin{cases} 
      1 & version = 2 \\
      0 & version = 1
   \end{cases}
   
$$

Where $X_1, X_2, X_3, X_4$ are Manual Dexterity, Aiming and Catching, Balance, and GAI respectively.

